---
title: "Developing Slurm Simulator: Micro3 Cluster, small trace"
author: nikolays@buffalo.edu
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document: 
    toc: yes
    toc_float: yes
    toc_depth: 2
    mathjax: null
    css: doc.css
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

setwd(path.expand("~/slurm_sim_ws/slurm_model/micro3simdev/analysis"))
library(stringr)
#library(rjson)
library(dplyr)
library(tibble)
library(lubridate)

#detach("package:RSlurmSimTools", unload=TRUE)
#devtools::document(path.expand("~/slurm_sim_ws/slurm_sim_tools/src/RSlurmSimTools"))
#devtools::install_local(path=path.expand("~/slurm_sim_ws/slurm_sim_tools/src/RSlurmSimTools"), force=TRUE)
library(RSlurmSimTools)


library(dplyr)
library(tidyr)
library(readr)
library(ggplot2)
library(cowplot)
#library(DepthProc)
#reticulate::source_python(file.path(system.file("python", package = "RSlurmSimTools"),"hostlist.py"))
#library(gplots)
#library(parallel)
library(plotly)
```


```{r}

read_sacct_out <- function(filename,nodes_desc=NULL,extract_node_list=FALSE){
    cat("Read: ",filename,"\n")
  
    if(grepl(".zst", filename, fixed=TRUE)){
      slurm_log <- data.table::fread(cmd=paste("zstdcat", filename),sep="|",header=TRUE)
    } else {
      slurm_log <- data.table::fread(filename,sep="|",header=TRUE)
    }
    
    #for(col in c("Submit","Eligible","Start","End","Elapsed","Timelimit",
    #             "Cluster","Partition","Account","Group","User", "ExitCode","State","QOS")){
        #cat(paste0(col,"S=",col,",\n"))
        #cat(paste0(col,"S,"))
    #}
    slurm_log <-  dplyr::rename(slurm_log,
        JobId=JobID,
        JobIdRaw=JobIDRaw,
        NodeCount=NNodes,
        SubmitS=Submit,
        EligibleS=Eligible,
        StartS=Start,
        EndS=End,
        ElapsedS=Elapsed,
        TimelimitS=Timelimit,
        ClusterS=Cluster,
        PartitionS=Partition,
        AccountS=Account,
        GroupS=Group,
        UserS=User,
        ExitCodeS=ExitCode,
        StateS=State,
        QOSS=QOS
    )
    #convert job names
    slurm_log$JobRecID <- as.integer(str_replace(slurm_log$JobName, "jobid_",""))
    
    #convert to proper format
    for(col in c("Submit","Eligible","Start","End")){
        slurm_log[[col]] <- as.POSIXct(slurm_log[[paste0(col,"S")]],format = "%Y-%m-%dT%H:%M:%S")
    }
    
    #duration
    for(col in c("Elapsed","Timelimit")){
        slurm_log[,col] <- extract_slurm_period(slurm_log[[paste0(col,"S")]])
    }
    
    #factor
    for(col in c("Cluster","Partition","Account","Group","User", "ExitCode","State","QOS")){
        slurm_log[,col] <- factor(slurm_log[[paste0(col,"S")]])
    }
    
    #state
    slurm_log$StateS <- as.character(slurm_log$StateS)
    slurm_log$StateS[grepl("CANCELLED",slurm_log$StateS)] <- "CANCELLED"
    slurm_log$State <- as.factor(slurm_log$StateS)
    
    #extract node list
    if(extract_node_list==TRUE){
        #python.load(file.path(rutil_dir,"..","src","hostlist.py"))
        #slurm_log$NodeListFull <- python.call("expand_hostlists_to_str",slurm_log$NodeList)
        slurm_log$NodeListFull <- expand_hostlists_to_list(slurm_log$NodeList)
    }

    #convert memory
    slurm_log$ReqMem[slurm_log$ReqMem=="0n"] <- "0Mn"
    reqmem <- stringr::str_match_all(slurm_log$ReqMem, "([\\.0-9]+)([MG])([nc]?)")
    
    reqmem_size <- sapply(reqmem,function(r){
        as.integer(r[[2]])
    })
    reqmem_unit <- sapply(reqmem,function(r)r[[3]])
    reqmem_perwhat <- sapply(reqmem,function(r)r[[4]])
    #convert to MB
    reqmem_size[reqmem_unit=="G"] <- reqmem_size[reqmem_unit=="G"]*1024
    
    slurm_log$ReqMemSize <- reqmem_size
    slurm_log$ReqMemPerNode <- reqmem_perwhat=="n" || reqmem_perwhat==""
    
    slurm_log$ReqMem <- NULL
    
    #set proper NA
    #slurm_log$ReqGRES[slurm_log$ReqGRES==""] <- NA
    if(!is.null(nodes_desc)){
      nr <- max(sapply(nodes_desc,function(n){length(n$Nodes)}))
      
      nodes_mat <- sapply(nodes_desc,function(n){c(n$Nodes,rep(NA,nr-length(n$Nodes)))})
      
      #assing nodes
      nodes_types_used <- sapply(slurm_log$NodeListFull,function(nodes){
        apply(nodes_mat,2,function(v){length(intersect(v,nodes))})
      })
      
      slurm_log <- cbind(slurm_log,t(nodes_types_used))
    }
    
    slurm_log$SubmitTS <- as.integer(slurm_log$Submit)
    slurm_log$StartTS <- as.integer(slurm_log$Start)
    slurm_log$EndTS <- as.integer(slurm_log$End)
    
    
    slurm_log$WaitHours <- as.integer(slurm_log$Start-slurm_log$Submit)/3600.0
    slurm_log$WaitHours[slurm_log$WaitHours<0.0] <- slurm_log$WaitHours[slurm_log$WaitHours<0.0]+1
    
    slurm_log$WallHours <- as.integer(slurm_log$Elapsed)/3600.0
    slurm_log$NodeHours <- slurm_log$WallHours*slurm_log$NodeCount
    
    #shift 0 value for log scales
    slurm_log$WaitHours4log <- slurm_log$WaitHours
    slurm_log$WaitHours4log[slurm_log$WaitHours4log<1/60]<-1/60
    #shift 0 value for log scales
    slurm_log$WallHours4log <- slurm_log$WallHours
    slurm_log$WallHours4log[slurm_log$WallHours4log<1/60]<-1/60
    
    slurm_log <- dplyr::arrange(slurm_log,SubmitTS)%>%
        dplyr::select(-c(SubmitS,EligibleS,StartS,EndS,ElapsedS,TimelimitS,ClusterS,
                         PartitionS,AccountS,GroupS,UserS,ExitCodeS,StateS,QOSS))
    
    min_time <- min(min(slurm_log$SubmitTS, na.rm=TRUE),min(slurm_log$StartTS, na.rm=TRUE),min(slurm_log$EndTS, na.rm=TRUE), na.rm=TRUE)
    
    slurm_log$SubmitTime <- slurm_log$SubmitTS - min_time
    slurm_log$StartTime <- slurm_log$StartTS - min_time
    slurm_log$EndTime <- slurm_log$EndTS - min_time
    slurm_log$WallTime <- slurm_log$EndTime - slurm_log$StartTime
    slurm_log$WaitTime <- slurm_log$StartTime - slurm_log$SubmitTime
    
    slurm_log <- relocate(slurm_log, JobRecID, SubmitTime, StartTime, EndTime, WallTime, WaitTime, .before = "JobId")
    
    return(slurm_log)
}

read_sacct_out_multiple <- function(slurm_mode, results_root_dir, dtstart_list, run_id_list, sacct_out="slurm_acct.out") {
  result_list <- list()
  for(dtstart in dtstart_list) {
    for(run_id in run_id_list) {
      m_result_root_dir <- path.expand(file.path(results_root_dir, paste0("dtstart_", dtstart, "_", run_id)))
      m_sacct_out_filename <- file.path(m_result_root_dir, sacct_out)
      
      if(!dir.exists(m_result_root_dir)) {
          warning(sprintf("Directory %s does not exists!", m_result_root_dir))
          return(NULL);
      }
      if(!file.exists(m_sacct_out_filename)) {
          if (file.exists(paste0(m_sacct_out_filename,".zst"))) {
              m_sacct_out_filename <- paste0(m_sacct_out_filename,".zst")
          } else {
              warning(sprintf("File %s does not exists!", m_sacct_out_filename))
              return(NULL);
          }
      }
      m_sacct_out <- read_sacct_out(m_sacct_out_filename)
      m_sacct_out$slurm_mode <- slurm_mode
      m_sacct_out$dtstart <- dtstart
      m_sacct_out$run_id <- run_id
      
      m_sacct_out <- relocate(m_sacct_out,slurm_mode,dtstart,run_id, .before = "JobRecID")
      result_list[[length(result_list)+1]] <- m_sacct_out
      
    }
  }
  return(data.table::rbindlist(result_list))
}

#JobName
# ../../../slurm_model_archive/micro3/bumblebee_1_351d4b6c2870284078531f082758f11116f0996d/small/
sacct <- bind_rows(
  read_sacct_out_multiple("b_0_tarball", path.expand("~/slurm_sim_ws/slurm_model_archive/micro3/bumblebee_21.08.04_tarball/small__ref"), c(58, 59, 68, 79, 89, 99, 105, 114, 126, 146), 1:2),
  read_sacct_out_multiple("b_1_351d", path.expand("~/slurm_sim_ws/slurm_model_archive/micro3/bumblebee_1_351d4b6c2870284078531f082758f11116f0996d/small"), c(58, 59, 68, 79, 89, 99, 105, 114, 126, 146), 1:2),
  #read_sacct_out_multiple("b_4_f588", path.expand("~/slurm_sim_ws/slurm_model/micro3simdev/results/bumblebee_4_f588c59c7a52c00c95f8c84c94e9122048c0acd0/small"), c(58, 59, 68, 79, 89, 99, 105, 114, 126, 146), 1:2),
  read_sacct_out_multiple("b_5_f588", path.expand("~/slurm_sim_ws/slurm_model/micro3simdev/results/bumblebee_5_f588c59c7a52c00c95f8c84c94e9122048c0acd0/small"), c(58, 59, 68, 79, 89, 99, 105, 114, 126, 146), 1),
  read_sacct_out_multiple("b_Z2_f588", path.expand("~/slurm_sim_ws/slurm_model/micro3simdev/results/bumblebee_2_f588c59c7a52c00c95f8c84c94e9122048c0acd0/small"), c(58, 59, 68, 79, 89, 99, 105, 114, 126, 146), 1:2),
  read_sacct_out_multiple("b_ZZ_f588", path.expand("~/slurm_sim_ws/slurm_model/micro3simdev/results/bumblebee/small"), c(58, 59), 1)
)
#sacct$rid <- sacct$run_id + sacct$dtstart*100
#sacct
#read_sacct_out(path.expand("~/slurm_sim_ws/slurm_model_archive/micro3/bumblebee_1_351d4b6c2870284078531f082758f11116f0996d/small/dtstart_58_1/slurm_acct.out"))
sacct
```
```{r}
jobs_summary <- sacct %>% group_by(slurm_mode,JobRecID) %>% summarise(
  SubmitTimeMean=mean(SubmitTime), SubmitTimeSD=sd(SubmitTime),
  StartTimeMean=mean(StartTime), StartTimeSD=sd(StartTime),
  WaitTimeMean=mean(WaitTime), WaitTimeSD=sd(WaitTime),
  WallTimeMean=mean(WallTime), WallTimeSD=sd(WallTime),
  .groups="drop_last"
) %>% arrange(JobRecID,slurm_mode)
jobs_summary
```
bumblebee_0_tarball - build from official tarball
bumblebee_1_351d4  - build from git using tag corresponding to above tarball, increased time accuracy in logs
bumblebee_2_f588c - first attempt to feed jobs from slurmctrld
bumblebee_3_f588c - same as 2 but feeding as in 1
bumblebee_4_f588c - same as 2 but feeding as in 1, also read trace but dont loop

read_sacct_out_multiple("bumblebee_1_351d4", path.expand("~/slurm_sim_ws/slurm_model_archive/micro3/bumblebee_1_351d4b6c2870284078531f082758f11116f0996d/small"), c(58, 59, 68, 79, 89, 99, 105, 114, 126, 146), 1:2),
  read_sacct_out_multiple("bumblebee_2_f588c"
```{r fig.width=11}
plot_grid(
  ggplot(jobs_summary, aes(x=JobRecID,y=StartTimeMean, fill=slurm_mode)) + 
    geom_bar(stat="identity", position=position_dodge()) + 
    theme(legend.position="bottom"),
  ggplot(jobs_summary, aes(x=JobRecID,y=StartTimeSD, fill=slurm_mode)) + 
    geom_bar(stat="identity", position=position_dodge()) + 
    theme(legend.position="bottom"),
  ggplot(jobs_summary, aes(x=JobRecID,y=WallTimeMean, fill=slurm_mode)) + 
    geom_bar(stat="identity", position=position_dodge()) + 
    theme(legend.position="bottom"),
  ggplot(jobs_summary, aes(x=JobRecID,y=WallTimeSD, fill=slurm_mode)) + 
    geom_bar(stat="identity", position=position_dodge()) + 
    theme(legend.position="bottom"),
  ncol=1)
```


```{r fig.width=11}
ggplot(sacct, aes(x=factor(JobRecID),y=StartTime, color=slurm_mode)) + 
    geom_boxplot(position=position_dodge()) + 
    theme(legend.position="bottom")
#ggplotly(p)
```

# Start Time Boxplot

```{r}
# 'max-width: 800px'
# "width: 100%; max-width: 800px;", width=1800
# plotlyOutput(width = "1800px")/usr/lib/R/site-library/plotly/htmlwidgets/lib/plotlyjs/plotly-latest.min.js:
plot_ly(sacct, x = ~factor(JobRecID), y = ~StartTime, color = ~slurm_mode, type = "box") %>% 
  layout(boxmode = "group", legend = list(orientation = 'h', y=-0.2))
```
```{r}
# 'max-width: 800px'
# "width: 100%; max-width: 800px;", width=1800
# plotlyOutput(width = "1800px")/usr/lib/R/site-library/plotly/htmlwidgets/lib/plotlyjs/plotly-latest.min.js:
plot_ly(sacct, x = ~factor(JobRecID), y = ~WallTime, color = ~slurm_mode, type = "box") %>% 
  layout(boxmode = "group", legend = list(orientation = 'h', y=-0.2))
```


```{r}
data(iris)

fig <- plot_ly()%>%
  add_trace(data = iris, x = ~Sepal.Width, y = ~Sepal.Length, color = ~Species, 
               type = "scatter", mode = "markers")%>%
  layout(title="Using The add_trace() method With A Plotly Figure",  legend=list(title=list(text='species')),
         plot_bgcolor='#e5ecf6', 
         xaxis = list( 
           zerolinecolor = '#ffff', 
           zerolinewidth = 2, 
           gridcolor = 'ffff'), 
         yaxis = list( 
           zerolinecolor = '#ffff', 
           zerolinewidth = 2, 
           gridcolor = 'ffff'))%>%
  add_trace(x = c(2, 4), y = c(4, 8), type = "scatter", mode = "lines", line = list(color = 'grey')
            , showlegend = FALSE)
fig
```

